Supplementary Tables

### 2019-09-23 Supplementary_additional_file.Rmd
article edit

---
title: "Supplementary Experimental Data File"
author: "Selcen Arı"
date: "22 09 2019"
output:
  pdf_document: default
  html_document: default
  word_document: default
bibliography: ref.bib
header-includes: 
  \usepackage{float} \floatplacement{figure}{H} 
  \newcommand{\beginsupplement}{\setcounter{table}{0}  \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0}     \renewcommand{\thefigure}{S\arabic{figure}}}
  \usepackage{subfig}
---

@@

library(tidygraph)
library(dplyr)
library(tidyr)
library(stringr)
library(readr)
library(readxl)

>>>>

---
title: "Supplementary Experimental Data File"
author: 
- Selcen Ari
- Alper Yilmaz 
date: "22 09 2019"
output:
  pdf_document: default
  html_document: default
  word_document: default
bibliography: ref.bib
header-includes: 
  \usepackage{float} \floatplacement{figure}{H} 
  \newcommand{\beginsupplement}{\setcounter{table}{0}  \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0}     \renewcommand{\thefigure}{S\arabic{figure}}}
  \usepackage{subfig}
---

@@

library(tidygraph)
library(dplyr)
library(tidyr)
library(stringr)
library(readr)
library(readxl)
knitr::opts_chunk$set(tidy.opts=list(width.cutoff=50),tidy=TRUE)

### 2019-09-23 Supplementary_figures.Rmd
article edit

---
title: "Supplementary Figures"
author: "Selcen Arı"
date: "17 09 2019"
output:
  pdf_document: default
  html_document: default
  word_document: default
bibliography: ref.bib
header-includes: 
  \usepackage{float} \floatplacement{figure}{H} 
  \newcommand{\beginsupplement}{\setcounter{table}{0}  \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0}     \renewcommand{\thefigure}{S\arabic{figure}}}
  \usepackage{subfig}
---

@@

library(tidygraph)
library(dplyr)
library(tidyr)
library(stringr)

@@

```{r, fig.cap= "Percentage of affected nodes of each iteration for SERPINE2 Gene"}
as.data.frame(E9GE_mirnagenenormal)%>%
 priming_graph(competing_count = GE_normal, miRNA_count = mirna_RPM, aff_factor = c(Energy, seed_type_effect), deg_factor = region_effect)%>%
 update_how("SERPINE2",2.75) %>%
 simulate(150) %>%
 find_iteration(limit=0, plot= TRUE) #limit=0 describes the change that is not taken into account.
```

>>>>

---
title: "Supplementary Figures"
author: 
- Selcen Ari
- Alper Yilmaz 
date: "17 09 2019"
output:
  pdf_document: default
  html_document: default
  word_document: default
bibliography: ref.bib
header-includes: 
  \usepackage{float} \floatplacement{figure}{H} 
  \newcommand{\beginsupplement}{\setcounter{table}{0}  \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0}     \renewcommand{\thefigure}{S\arabic{figure}}}
  \usepackage{subfig}
---

@@

library(tidygraph)
library(dplyr)
library(tidyr)
library(stringr)
knitr::opts_chunk$set(tidy.opts=list(width.cutoff=50),tidy=TRUE)

@@

```{r, fig.cap= "Percentage of affected nodes of each iteration for SERPINE2 Gene"}
as.data.frame(E9GE_mirnagenenormal)%>%
 priming_graph(competing_count = GE_normal, miRNA_count = mirna_RPM, aff_factor = c(Energy, seed_type_effect), deg_factor = region_effect)%>%
 update_how("SERPINE2",2.75) %>%
 simulate(150) %>%
 find_iteration(limit=1, plot= TRUE) 
#limit=0 describes the change that is not taken into account.
```

### 2019-09-23 Supplementary_mat_met.Rmd
article edit

---
title: "Supplementary Materials And Methods"
author: "Selcen Ari"
date: "7 Nisan 2019"
output:
  pdf_document: default
  html_document: default
  word_document: default
bibliography: ref.bib
header-includes: 
  \usepackage{float} \floatplacement{figure}{H} 
  \newcommand{\beginsupplement}{\setcounter{table}{0}  \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0}     \renewcommand{\thefigure}{S\arabic{figure}}}
  \usepackage{subfig}
---

@@

library(tidygraph)
library(dplyr)
library(tidyr)
library(stringr)

@@

```{r, echo=FALSE, message= FALSE, warning=FALSE}
# Install the packages which is necessary to obtain and process datasets.
#install.packages("BiocManager")
#BiocManager::install("SummarizedExperiment")
#BiocManager::install("TCGAbiolinks")
library(TCGAbiolinks)
library(SummarizedExperiment)
```

@@

```{r, message= FALSE, warning=FALSE}
library(readr)
read_tsv("hsa_mirna.txt", comment = "#", col_names = FALSE)%>%
  dplyr::select(mirna_type= X3, definition = X9)%>%
  filter(!endsWith(mirna_type, "primary_transcript"))%>%
  tidyr::separate(definition, c("ID", "Alias", "Name", "Derivated"), sep = ";")%>%
  dplyr::select(Alias, Name)%>%
  tidyr::separate(Alias, c("trash1", "ID"), sep = "=")%>%
  tidyr::separate(Name, c("trash2", "Name"), sep = "=")%>%
  dplyr::select(-trash1, -trash2)-> mirbase_id_conv

@@

```{r}
library(ceRNAnetsim)
as.data.frame(E9GE_mirnagenenormal)%>%
 priming_graph(competing_count = GE_normal, miRNA_count = mirna_RPM, aff_factor = c(Energy, seed_type_effect), deg_factor = region_effect)%>%
 update_how("SERPINE2",2.75)%>%
 simulate(50) %>%
 find_iteration(limit=0, plot= FALSE)

@@

```{r}
as.data.frame(E9GE_mirnagenenormal)%>%
  priming_graph(competing_count = GE_normal, miRNA_count = mirna_RPM, aff_factor = c(Energy, seed_type_effect), deg_factor = region_effect)%>%
  update_how("SERPINE2",2.75)%>%
  simulate(32)

@@

```{r}
as.data.frame(E9GE_mirnagenenormal)%>%
  priming_graph(competing_count = GE_normal, miRNA_count = mirna_RPM, aff_factor = c(Energy, seed_type_effect), deg_factor = region_effect)%>%
  update_how("SERPINE2",2.75)%>%
  simulate(32)%>%
  as_tibble()%>%
  dplyr::select(name, initial_count, count_current)->simulation_results
```

@@

# 3. REFERENCES

>>>>

---
title: "Supplementary Materials And Methods"
author: 
- Selcen Ari
- Alper Yilmaz 
date: "7 Nisan 2019"
output:
  pdf_document: default
  html_document: default
  word_document: default
bibliography: ref.bib
header-includes: 
  \usepackage{float} \floatplacement{figure}{H} 
  \newcommand{\beginsupplement}{\setcounter{table}{0}  \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0}     \renewcommand{\thefigure}{S\arabic{figure}}}
  \usepackage{subfig}
---

@@

library(tidygraph)
library(dplyr)
library(tidyr)
library(stringr)
library(readr)
knitr::opts_chunk$set(tidy.opts=list(width.cutoff=50),tidy=TRUE)

@@

```{r, echo=FALSE, message= FALSE, warning=FALSE, eval=FALSE}
# Install the packages which is necessary to obtain and process datasets.
#install.packages("BiocManager")
#BiocManager::install("SummarizedExperiment")
#BiocManager::install("TCGAbiolinks")
library(TCGAbiolinks)
library(SummarizedExperiment)
```

@@

read_tsv("hsa_mirna.txt", comment = "#", col_names = FALSE)%>%
  dplyr::select(mirna_type= X3, definition = X9)%>%
  filter(!endsWith(mirna_type, "primary_transcript"))%>%
  tidyr::separate(definition, c("ID", "Alias", "Name", "Derivated"), sep = ";")%>%
  dplyr::select(Alias, Name)%>%
  tidyr::separate(Alias, c("trash1", "ID"), sep = "=")%>%
  tidyr::separate(Name, c("trash2", "Name"), sep = "=")%>%
  dplyr::select(-trash1, -trash2)-> mirbase_id_conv

@@

```{r}

as.data.frame(E9GE_mirnagenenormal)%>%
 priming_graph(competing_count = GE_normal, miRNA_count = mirna_RPM, aff_factor = c(Energy, seed_type_effect), deg_factor = region_effect)%>%
 update_how("SERPINE2",2.75)%>%
 simulate(50) %>%
 find_iteration(limit=1, plot= FALSE)

@@

```{r}
as.data.frame(E9GE_mirnagenenormal)%>%
  priming_graph(competing_count = GE_normal, miRNA_count = mirna_RPM, aff_factor = c(Energy, seed_type_effect), deg_factor = region_effect)%>%
  update_how("SERPINE2",2.75)%>%
  simulate(62)

@@

```{r}
as.data.frame(E9GE_mirnagenenormal)%>%
  priming_graph(competing_count = GE_normal, miRNA_count = mirna_RPM, aff_factor = c(Energy, seed_type_effect), deg_factor = region_effect)%>%
  update_how("SERPINE2",2.75)%>%
  simulate(62)%>%
  as_tibble()%>%
  dplyr::select(name, initial_count, count_current)->simulation_results
```

@@

### 2019-09-23 Supplementary_tables.Rmd
article edit

---
title: "Supplementary Tables"
author: "Selcen Arı"
date: "16 09 2019"
output:
  pdf_document: default
  html_document: default
  word_document: default
bibliography: ref.bib
header-includes: 
  \usepackage{float} \floatplacement{figure}{H} 
  \newcommand{\beginsupplement}{\setcounter{table}{0}  \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}}
---

```{r, eval=FALSE, include=FALSE}
#install.packages("kable")
library(xtable)
```

@@

@@

@@

|Variebles| Structure | Means|
|-----------|------------|------------|
| **Node Variables**
| `name`  | character | node name |
| `type`  | character |Competing or miRNA |
| `node_id`  | numeric | in on graph object |
| `initial_count`   | numeric | Initial Expression value of node |
| `count_pre`   | numeric | Expression value of node at previous regulation |
| `count_current`   | numeric | Existing expression value of node |
| `changes_variable`   | character | Regulation of node (Up, down or steady) |
|-----------|------------|------------|
| **Edge Variables**
| `Competing name` | character | name of genes|
| `miRNA name` | character | name of miRNAs|
| `Competing expression` | numeric | Expression values of competing elements at steady-state |
| `miRNA expression` | numeric | Expression values of miRNA elements at steady-state |
| `energy` | numeric | coefficient of miRNA:target interactions (binding affinity)|
| `seed type` | numeric | coefficient of miRNA:target interactions (binding affinity)|
| `region` | numeric | coefficient of miRNA:target interactions (degradation efficiency)|
| `afff factor` | numeric| coefficient scaled and combined affinity factor |
| `degg factor` | numeric |coefficient scaled and combined degradation factor| 
| `comp_count_list` | list | list of competing expression for each iteration | 
| `comp_count` | numeric | _pre: competing expression at previous iteration; _current: competing expression at present iteration |
| `mirna_count_list` | list | list of miRNA expression for each iteration | 
| `mirna_count` | numeric | _pre: miRNA expression at previous iteration; _current: miRNA expression at present iteration |
| `effect` | numeric | _pre: total miRNA reppressive effect on individual target at previous iteration ; _current: miRNA reppressive effect on individual target at present iteration |
| `effect_list` | list | list of miRNA reppressive effect on individual target for each iteration |

Table: The context graph object during the process.

>>>>

---
title: "Supplementary Tables"
author: 
- Selcen Ari
- Alper Yilmaz 
date: "16 09 2019"
output:
  pdf_document: default
  html_document: default
  word_document: default
bibliography: ref.bib
header-includes: 
  \usepackage{tabularx}
  \usepackage{float}
  \usepackage{caption}
  \newcommand{\beginsupplement}{\setcounter{table}{0}  \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}}
---

@@

```{r, eval=FALSE, include=FALSE}
library(xtable)
knitr::opts_chunk$set(tidy.opts=list(width.cutoff=50),tidy=TRUE)
library(gt)

```

@@

 \begin{table}[ht]
\centering
\caption{ miRNA:target pairs supported by High-throughput Experiments}
\begin{tabular}{lll}
  \hline
 Variable & Structure & Means \\
  \hline
   cluster    & character & Barcode from experimentally method \\
   chromosome    & character & Chromosome of Terget gene from raw data \\
   start\_position    & numeric & Gene start position from raw data \\
   end\_position     & numeric & Gene end position from raw data \\
   strand     & chracter & Gene strand \\
   hgnc\_symbol     & character & Gene name (Symbol) \\
   Ensembl\_Gene\_Id     & character & Ensembl Gene Id of gene \\
   Ensembl\_Transcript\_Id   & character & Ensembl transcript id of mRNA of Target gene \\
   target\_seq   & character & mRNA sequences targeted by miRNA \\
   miRNA   & character & miRNA id (from miRBase vesion 21 ) \\
   miR\_seq   & character & miRNA sequence \\
   seed\_type   & character & seed type of miRNA:target interaction \\
   Energy   & numeric & Energy of miRNA:target binding \\
   HG38build\_loc   & character & Recent chromosomal location of Gene \\
   Genom\_build   & character& Genom build of given chromosome, start and end positions \\
   region   & character & interaction location on target \\ 
   region\_effect   & numeric & Coefficient of location on target \\ 
   seed\_type\_effect   & numeric & Coefficient for seed sequence of miRNA:target interaction \\
   \hline
\end{tabular}
\end{table}

@@

 \begin{table}[ht]
\centering
\caption{ The context graph object during the process.}
\begin{tabularx}{\textwidth}{llX}
  \hline
 Variables & Structure & Means \\
  \hline
   \emph{Node Variables} & & \\
   name    & character & node name \\
   type    & character &Competing or miRNA \\
   node\_id    & numeric & in on graph object \\
   initial\_count     & numeric & Initial Expression value of node \\
   count\_pre     & numeric & Expression value of node at previous regulation \\
   count\_current     & numeric & Existing expression value of node \\
   changes\_variable     & character & Regulation of node (Up, down or steady) \\
   \hline
   \emph{Edge Variables} & & \\
   Competing name   & character & name of genes\\
   miRNA name   & character & name of miRNAs \\
   Competing expression   & numeric & Expression values of competing elements at steady-state \\
   miRNA expression   & numeric & Expression values of miRNA elements at steady-state \\
   energy   & numeric & coefficient of miRNA:target interactions (binding affinity) \\
   seed type   & numeric & coefficient of miRNA:target interactions (binding affinity) \\
   region   & numeric & coefficient of miRNA:target interactions (degradation efficiency) \\
   afff factor   & numeric& coefficient scaled and combined affinity factor \\
   degg factor   & numeric &coefficient scaled and combined degradation factor \\ 
   comp\_count\_list   & list & list of competing expression for each iteration \\ 
   comp\_count   & numeric & pre: competing expression at previous iteration; current: competing expression at present iteration \\
   mirna\_count\_list   & list & list of miRNA expression for each iteration \\
   mirna\_count   & numeric & pre: miRNA expression at previous iteration; current: miRNA expression at present iteration \\
   effect   & numeric & pre: total miRNA reppressive effect on individual target at previous iteration ; current: miRNA reppressive effect on individual   target at present iteration \\
   effect\_list   & list & list of miRNA reppressive effect on individual target for each iteration \\
  \hline
\end{tabularx}
\end{table}

\newpage
